Body Image and Trikafta

### 2025-08-04 Emily Muther/body_image_trikafta.qmd
added adherence to table 1

```{r}
#| label: demographics
normal_dist <- c("FEV1", "Age", "BMI")
df %>%
  select(
    PHQ9_Total, PHQ9_category, GAD7_Total, GAD7_category, FRStotal,
    FRS_IdealBody, FRS_ThinkyouLook, FRS_Category, Age, Gender, Race,
    Ethnicity, InsuranceType, BMI, bmi_raw, FEV1, BE_APPEARANCE_MEAN,
    BE_ATTRIBUTION_MEAN, BE_WEIGHT_MEAN
  ) %>%
  tbl_summary(
    by = Gender,
    type = list(
      c("FRStotal", "FRS_IdealBody", "FRS_ThinkyouLook", "bmi_raw") ~ "continuous2",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~ c(
        "{median} [{p25}, {p75}]",
        "{min}, {max}"
      ),
      all_of(normal_dist) ~ c("{mean} ({sd})", "{min}, {max}")
    ),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(all_of(normal_dist) ~ "t.test"),
    test.args = all_tests("wilcox.test") ~ list(exact = F)
  ) %>%
  separate_p_footnotes()
```

>>>>

```{r}
#| label: demographics
normal_dist <- c("FEV1", "Age", "BMI")
df %>%
  select(
    PHQ9_Total, PHQ9_category, GAD7_Total, GAD7_category, FRStotal,
    FRS_IdealBody, FRS_ThinkyouLook, FRS_Category, Age, Gender, Race,
    Ethnicity, InsuranceType, BMI, bmi_raw, FEV1, BE_APPEARANCE_MEAN,
    BE_ATTRIBUTION_MEAN, BE_WEIGHT_MEAN, contains("Adherence")
  ) %>%
  mutate(
    PercentAdherence = as.numeric(sub("%", "", as.character(PercentAdherence))),
    over80 = PercentAdherence >= 80
  ) %>%
  tbl_summary(
    by = Gender,
    type = list(
      c("FRStotal", "FRS_IdealBody", "FRS_ThinkyouLook", "bmi_raw", "PercentAdherence") ~ "continuous2",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~ c(
        "{median} [{p25}, {p75}]",
        "{min}, {max}"
      ),
      all_of(normal_dist) ~ c("{mean} ({sd})", "{min}, {max}")
    ),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(all_of(normal_dist) ~ "t.test"),
    test.args = all_tests("wilcox.test") ~ list(exact = F)
  ) %>%
  separate_p_footnotes()
```
